### 2022-10-20 types.tex
some late-night realization notes

>>>>

Another important note! I think fold/unfold are wrong and unfit for purpose, actually.  We should really be replacing the variable names with their derivation expression when they're placed into the derivation context for the first time.  But as of right now, that's not how the type system works.  Maybe we need to "output" a derivation, rather than put it in the context.  Note: doing this naively immediately breaks on the dispatch to relevant-parallel and general-parallel.  I think it still holds significant promise, but might not be viable for 11:40pm.
